
\subsection{Control register files}
\label{sec:core-ug-cfg-cregs}

The control register file configuration files reside in the \code{config/cregs}
directory of the \rvex{} repository. The configuration consists of a set of
LaTeX-styled files, interpreted ordered alphabetically by their filenames. The
configuration controls roughly the following things.

\begin{itemize}

\item The address of each control register, within hardcoded limits. The global
      register file is mapped from \code{0x000} to \code{0x100}, whereas the
      context control register file is mapped from \code{0x200} to \code{0x400}.

\item The documentation for each control register, as it appears in
      Sections~\ref{sec:core-ug-creg-gb} and \ref{sec:core-ug-creg-cx} of this
      manual.
      
\item The functionality of each register, described using a special C-like
      language, which may be compiled to VHDL and C. The latter is intended for
      a cycle-accurate simulator, but this does not exist yet.
      
\item The VHDL entity interface of the \rvexent{cxreg} and \rvexent{gbreg},
      such that the implementations of the registers can communicate with the
      rest of the processor. If the interface is changed, the instantiation of
      \rvexent{cxreg} and \rvexent{gbreg} in \code{core.vhd} must be changed
      accordingly to make the connections.

\end{itemize}

\noindent The first of the following sections describes the LaTeX-style commands 
that are recognized by the configuration scripts. Any other commands are 
interpreted as being part of the LaTeX documentation sections. The remaining 
sections document the `language-agnostic' mini-language used to describe the 
register logic implementations. This language-agnostic code can be transformed 
by the configuration scripts into both VHDL for the hardware and C for a 
simulator, although the latter is not yet utilized.

\subimport{1-cref/}{core-ug-cfg-cregs-cref.tex}
\subimport{2-code/}{core-ug-cfg-cregs-code.tex}
\subimport{3-types/}{core-ug-cfg-cregs-types.tex}
\subimport{4-predef/}{core-ug-cfg-cregs-predef.tex}
\subimport{5-literals/}{core-ug-cfg-cregs-literals.tex}
\subimport{6-refs/}{core-ug-cfg-cregs-refs.tex}
\subimport{7-ops/}{core-ug-cfg-cregs-ops.tex}
\subimport{8-stmts/}{core-ug-cfg-cregs-stmts.tex}
