
\globalInterface{}

%===============================================================================
\ifaceGroup{Run control}
%===============================================================================
\ifaceSubGroup{}
\ifaceOut{rv}{reset}{bit}{0}
Reset output. This can be made high for one cycle by the debug bus writing a one
to the MSB of GSR.

%===============================================================================
\ifaceGroup{Interface with configuration logic}
%===============================================================================
\ifaceSubGroup{}
\ifaceOut{cfg}{requestData}{data}{0}
\ifaceOut{cfg}{requestEnable}{bit}{0}
Each nibble in the data word corresponds to a pipelane group, of which bit 3 
specifies whether the pipelane group should be disabled (high) or enabled (low) 
and, if low, bit 2..0 specify the context it should run on. Bits which are not 
supported by the core (as specified in the CFG generic) should be written zero 
or the request will be ignored (as specified by the error flag in the global 
control register file). The enable signal is active high.

\ifaceSubGroup{}
\ifaceIn{cfg}{currentCfg}{data}
Current configuration, using the same encoding as the request data.
    
\ifaceSubGroup{}
\ifaceIn{cfg}{busy}{bit}
Configuration busy signal. When set, new configuration requests are not 
accepted.
    
\ifaceSubGroup{}
\ifaceIn{cfg}{error}{bit}
Configuration error signal. This is set when the last configuration request was 
erroneous.
    
\ifaceSubGroup{}
\ifaceIn{cfg}{requesterID}{bitvec4}
When reconfiguration is requested, this field is set to the index of the context 
which requested the configuration, or all ones if the source was the debug bus.

%===============================================================================
\ifaceGroup{Interface with memory}
%===============================================================================
\ifaceSubGroup{}
\ifaceIn{imem}{affinity}{data}
Affinity signal from the memory.

%===============================================================================
\ifaceGroup{Misc.}
%===============================================================================
\ifaceSubGroup{}
\ifaceIn{rv}{coreID}{byte}
Core ID generic, passed as a port because of limitations in the register
generator.

\ifaceSubGroup{}
\ifaceIn{rv}{platformTag}{bitvec56}
ASCII platform tag code for the platform version registers.

