
%===============================================================================
\register{GSR}{Global status register}{0x000}
%===============================================================================

This register contains miscellaneous status information.

%-------------------------------------------------------------------------------
\field{31}{R}
%-------------------------------------------------------------------------------
Reset flag. The entire \rvex{} processor will be reset when the debug bus writes
a one to this flag. Writing a zero has no effect.

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\implementation{}

%-------------------------------------------------------------------------------
\field{13}{E}
%-------------------------------------------------------------------------------
Reconfiguration error flag. This flag is set by hardware when an invalid
configuration was requested. It is cleared once a valid configuration is
requested.

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\implementation{}

%-------------------------------------------------------------------------------
\field{12}{B}
%-------------------------------------------------------------------------------
Reconfiguration busy flag. While high, reconfiguration requests are ignored.

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\implementation{}

%-------------------------------------------------------------------------------
\field{11..8}{RID}
%-------------------------------------------------------------------------------
Reconfiguration requester ID. When a configuration is requested, this field is
set to the context ID of the context that requested the configuration, or to
0xF if the request was from the debug bus. This may be used by the
reconfiguration sources to see if they have won arbitration. Refer to
Section~\ref{sec:core-ug-reconf-request} for more information.

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\implementation{}

%===============================================================================
\register{BCRR}{Bus reconfiguration request register}{0x004}
%===============================================================================

This register may be written to by the debug bus only. When it is written, a
reconfiguration is requested. Refer to Sections~\ref{sec:core-ug-reconf-word}
and \ref{sec:core-ug-reconf-request} for more information.

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\field{31..0}{BCRR}
\implementation{}

%===============================================================================
\register{CC}{Current configuration register}{0x008}
%===============================================================================

This register is hardwired to the current configuration vector. Refer to
Section~\ref{sec:core-ug-reconf-word} for more information.

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\field{31..0}{CC}
\implementation{}

%===============================================================================
\register{AFF}{Cache affinity register}{0x00C}
%===============================================================================

This register stores the cache block index (akin to a lane group) that most
recently serviced an instruction fetch for a given context. This may be used for
achieving the maximum possible instruction cache locality when reconfiguring.

Each nibble represents a lane group. The nibble value is the context index.

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\field{31..0}{AF}
\implementation{}
